\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
% \usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry}
% Select font (comment out lines 6-9 to use Computer Modern)
% \usepackage{charter}
% \usepackage[default]{lato}
% \usepackage[sfdefault]{carlito}
% \usepackage{tgpagella}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

\begin{document}

\centerline{\Huge Jamie Pinnington}
\centerline{jpinnington7@gmail.com | linkedin.com/in/jamie-pinnington | github.com/jpinn97}

\section*{Education}
\textbf{Canterbury Christ Church University} -- BSc in Computer Science \hfill Expected May 2024 \\
\textbf{The Open University} -- Certificate of Higher Education in Computing and IT \hfill Oct 2016 - Jun 2017

\vspace{-4.5pt}

\section*{Experience}
\textbf{Team Leader} \hfill Kent \\
Food Retail, The Co-op \hfill May 2022 -- Present \\
\vspace{-10pt}
\begin{itemize}
  \item An exceeding person in control of a convenience store of excellence, demonstrated strong leadership overseeing a team of 5+ staff.
  \item Stringent compliance of policy by effective usage of staff, monitoring store performance, implementing and improving store objectives, resulting in a YoY revenue increase from £2.5 to £5.6+ million.
\end{itemize}

\textit{Customer Team Member} \hfill October 2021 -- May 2022
\vspace{-10pt}
\begin{itemize}
  \item Demonstrated exceptional work ethic and reliability, ensuring all tasks were performed accurately and efficiently, contributing to consistently high store standards and customer satisfaction in a fast-paced retail environment.
\end{itemize}

\textbf{Reserve Officer Cadet} \hfill Canterbury \\
British Army, Armed Forces \hfill Oct 2021 -- Jul 2022 \\
\vspace{-10pt}
\begin{itemize}
  \item Utilized prior military experience to assist and support senior-officers in the training and development of Officer Cadets on Module A of the British Army Officer training course through fieldcraft and weapon handling.
\end{itemize}

\textbf{Day Trader} \hfill Kent \\
Self-employed \hfill Aug 2020 -- Jan 2022 \\
\vspace{-10pt}
\begin{itemize}
  \item Trading American markets, primarily high-frequency momentum trading to grow a personal investment portfolio from £3,000 to £60,000+
\end{itemize}

\textbf{Regular} \hfill Pirbright, Surrey \\
British Army, Armed Forces\hfill May 2021 -- Aug 2021 \\
\vspace{-10pt}
\begin{itemize}
  \item Awarded 'Best Shot' for outstanding marksmanship and precision, demonstrating exceptional skill and focus in firearm handling during Phase 1 training.
  \item Recognized as 'Most Improved' recruit, showcasing remarkable progress and dedication to personal and professional development throughout the training period.
\end{itemize}

\textbf{Customer Team Member} \hfill Kent \\
Food Retail, The Co-op \hfill May 2019 -- Dec 2019 \\
\vspace{10pt}

\textbf{Sales Advisor} \hfill Kent \\
Superdrug \hfill Nov 2017 -- May 2019 \\
\vspace{10pt}

\vspace{-16.5pt}

\section*{Projects}
\textbf{AI-based ASL Fingerspelling Recognition for Automated Kiosk Transactions} \hfill Present \\
\vspace{-10pt}
\begin{itemize}
  \item Using PyTorch and TensorFlow to develop a Transformer-based model to recognize and translate American Sign Language fingerspelling to text.
  \item Building a desktop application using Mediapipe to perform real-time inference on webcam input.
\end{itemize}

\textbf{CRUD SPA} \hfill github.com/jpinn97/frameworks\_and\_languages\_module \\
\vspace{-10pt}
\begin{itemize}
  \item Developed a RESTful single-page application using React, TypeScript, and Tailwind CSS, with a Go and Gin backend.
  \item The two individual services were containerized using Docker and minimized using multi-stage builds for the lightest possible image.
\end{itemize}

\textbf{Utility Script} \hfill github.com/jpinn97/utility\_script-jpinn97 \\
\vspace{-10pt}
\begin{itemize}
  \item Developed a versatile Bash utility script featuring UUID generation (Version 1 and 4), process monitoring, and file analysis.
  \item Integrated C and Python components for advanced functionality and created a comprehensive man page for user guidance.
\end{itemize}

\textbf{Discovery Park Skills Hub} \hfill github.com/jpinn97/discovery-skillhub-cccu
\vspace{-10pt}
\begin{itemize}
  \item First place prototype web application for Discovery Park's Skills Hub.
  \item Used WordPress, JavaScript and PHP to develop a CMS solution befitting the client's requirements.
\end{itemize}

\textbf{Self-hosted Website} Personal \hfill jamie-pinnington.co.uk \hfill Present \\
\vspace{-10pt}
\begin{itemize}
  \item Using GIN, HTMX, and Templ to serve a static website on a Raspberry Pi 5 to learn greater depths of web development.
  \item Running a full BTC node on the same device to support the Bitcoin network, in addition to serving the Remote Weather Collector.
\end{itemize}

\textbf{Remote Weather Collector} Personal \hfill Present \\
\vspace{-10pt}
\begin{itemize}
  \item Designing and building a weather station using a Raspberry Zero 2 W, that will run remotely via a solar panel and LoRa to collect weather data and imagery.
\end{itemize}

\section*{Skills}
\begin{description}
  \item[] \textbf{Technical Languages:} Latex, Python, Go, TypeScript, Bash, C\#, Markdown, R, Tailwind
  \item[] \textbf{Frameworks \& Libraries} Git, TensorFlow, PyTorch, Keras, React, Gin, Next.js, Vite, Pandas, REST, RStudio
  \item[] \textbf{Technologies:} Docker, WSL, Linux, Jira, Jupyter Notebooks,
\end{description}

\section*{Voluntary Work}
\begin{itemize}
  \item \textbf{Lvl 3 Computer Science Course Representative} Providing support to Computer Science students, and forwarding issues internally.
  \item \textbf{Student Assistant} Building and researching student guidance for Canterbury Christ Church University as apart of a team for academic usage of generative AI.
\end{itemize}
% \section*{Projects}
% \begin{itemize}
%   \item \textbf{QuantSoftware Toolkit:} Open source Python library for data analysis and machine learning for finance
%   \item \textbf{GitHub Visualization:} Data visualization of Git Log data using D3 to analyze project trends over time
%   \item \textbf{Recommendation System:} Music and movie recommender systems using collaborative filtering on public datasets
%   \item \textbf{Mac Setup:} Book that gives step by step instructions on setting up developer environment on Mac OS
% \end{itemize}

\vspace{-16.5pt}

\end{document}
